Methods paper for erosion

### 2017-10-10 docs/methods/erosion_methods.tex
Working on methods latex, section theta-L.
Working on theta-L in methods papers

\vsp{2}
To handle boundary evolution, we use the {\thL}    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems. Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).

In order to regularize boundary evolution, we modify the normal velocity in Eq.~(\ref{eqn:bodyEvolution}) as follows
\begin{equation}
\Vn = \abs{\tau} + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body. The second term on the right acts to smooth bodies that have high-frequency oscillations. Since we have subtracted the mean curvature, $2\pi/L$, this term is area-preserving, so that the only material loss is due to the shear stress. We chose the prefactor $\log^{-1} \left(2\pi/L \right)$, so that, for 2D Stokes flow, this term scales the same as shear stress as $L \to 0$. Thus, the relative strength of the smoothing is always the same.

We now introduce the tangent angle, $\theta$, defined through the relation
\begin{equation}
(x_s, y_s) = (\cos \theta, \sin \theta)
\end{equation}
where $s$ is arc length. We also introduce the normalized arc length $\alpha = s / L$. In terms of these new variables, the curvature can be expressed as
\begin{equation}
\kappa = \frac{1}{L} \pderiv{\theta}{\alpha}
\end{equation}
Substitution into Eq.~(\ref{})

>>>>

\vsp{2}
To handle boundary evolution, we use the {\thL}    method, which offers certain advantages in the ability to stabilize fluid-structure interaction problems \cite{hou-low-she1994}. Throughout this section, we use the following conventions: the bodies are parametrized in the CCW direction and the normal vector points into the bodies (our out of the fluid).

In order to regularize boundary evolution, we modify the normal velocity in Eq.~(\ref{eqn:bodyEvolution}) as follows
\begin{equation}
\label{eqn:Vn}
\Vn = \atau + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body. The second term on the right acts to smooth bodies that have high-frequency oscillations. Since we have subtracted the mean curvature, $2\pi/L$, this term is area-preserving, so that the only material loss is due to the shear stress. We chose the prefactor $\log^{-1} \left(2\pi/L \right)$, so that, for 2D Stokes flow, this term scales the same as shear stress as $L \to 0$. Thus, the relative strength of the smoothing is always the same.

We now introduce the tangent angle, $\theta$, defined through the relation
\begin{equation}
(x_s, y_s) = (\cos \theta, \sin \theta)
\end{equation}
where $s$ is arc length. We also introduce the normalized arc length $\alpha = s / L$. In terms of these new variables, the curvature can be expressed as
\begin{equation}
\kappa = \frac{1}{L} \pderiv{\theta}{\alpha}
\end{equation}
Substitution into Eq.~(\ref{eqn:Vn}) gives
\begin{equation}
\label{eqn:Vn2}
\Vn = \atau + \frac{\eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 2 \pi \right)
\end{equation}
The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced. The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
\begin{equation}
\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
\end{equation}
The interface evolution is then given by
\begin{equation}
\dot{\xx}(t) = \Vn \nn + \Vs \ss.
\end{equation}
Upon transforming to the variables $\theta(\alpha,t)$ and $L(t)$, we obtain the evolution equations
\begin{align}
& \tderiv{L}{t} = - \mean{\thalpha \Vn} \\
& \pderiv{\theta}{t} = L^{-1} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
\end{align}
Inserting Eq.~(\ref{eqn:Vn2}) for the normal velocity gives
\begin{equation}
\pderiv{\theta}{t} = \frac{\eps}{L^{2} \log \left(2\pi/L \right)} \ppd{\theta}{\alpha} 
+ \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
\end{equation}
For simplicity, we introduce the variables
\begin{align}
& M = - \mean{\thalpha \Vn} \\
& N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
& \elfun(L) = \frac{1}{L^{2} \log \left(2\pi/L \right)}
\end{align}
Then the evolution equations can be expressed as
\begin{align}
& \tderiv{L}{t} = M \\
& \pderiv{\theta}{t} = \eps \elfun(L) \ppd{\theta}{\alpha} + N
\end{align}
We treat $\theta$ spectrally
\begin{equation}
\theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha}
\end{equation}
Then we get
\begin{equation}
\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun(L) \thhat_k = \hat{N}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun(L) dt \right)
\end{equation}
so that the solution can be represented as
\begin{align}
\thhat_k(t) & = \frac{1}{\mu} \int \mu \hat{N}_k dt 
= \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun(L) dt'' \right) \hat{N}_k \, dt'
% LONGER FORM
%& = \exp \left( -4 \eps \pi^2 k^2 \int_0^t \elfun(L) ds \right) \, 
%\int_0^t \exp \left( 4 \eps \pi^2 k^2 \int_0^s \elfun(L) ds' \right) \hat{N}_k ds \\
\end{align}
where $t'$ and $t''$ are simply dummy variables for integration. We can get the exact relationship
\begin{equation}
\thhat_k(t + \Delta t) = \thhat_k(t) + \int_t^{t+\Delta t}
\end{equation}
